---
title: "Links to PPP Loan Totals by State"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r maketable, echo=FALSE,warning=FALSE,message=FALSE}
library(tidycensus)
library(rvest)
library(tidyverse)
library(janitor)
library(kableExtra)
census_api_key("549950d36c22ff16455fe196bbbd01d63cfbe6cf")

population_state<- get_acs(geography="state", variables=c("B01001_001"),geometry = FALSE, year=2019) %>%
  clean_names() %>%
  select(state = name,
         population=estimate) 

ppp_totals_by_state_url <- "https://projects.propublica.org/coronavirus/bailouts/"

ppp_totals_by_state <- ppp_totals_by_state_url %>%
  read_html() %>%
  html_table()

ppp_totals_by_state <- ppp_totals_by_state[[1]] %>%
  clean_names() %>%
  mutate(total_ppp_loans=parse_number(total)) %>%
  select(state,total_ppp_loans) %>%
  inner_join(population_state) %>%
  mutate(clean_state = str_replace_all(tolower(state)," ","_"))

state_list <- ppp_totals_by_state$clean_state

#state_list <- state_list[[38]]

```


```{r runloop, eval=FALSE, echo=FALSE,warning=FALSE,message=FALSE}
#```{r runloop, eval=TRUE, echo=FALSE,warning=FALSE,message=FALSE}

# Swap comments to generate
for (state_name in state_list) {
  
  indv_state <- ppp_totals_by_state %>%
    filter(clean_state == state_name) %>%
    select(-clean_state)
  
  indv_state
  
rmarkdown::render(input = "ppp_template.Rmd", 
                  output_format = "html_document",
                  output_file = paste0(state_name,".html"),
                  output_dir = "states/")
  
}


```

```{r makelanding, eval=TRUE, echo=FALSE,warning=FALSE,message=FALSE}
#```{r makelanding, eval=FALSE, echo=FALSE,warning=FALSE,message=FALSE}


links_table <- ppp_totals_by_state %>%
  mutate(url = paste0("https://smussenden.github.io/coursefiles/ppp_scraping_example/states/",clean_state,".html")) %>%
  mutate(state_page_link = paste0("<a href='", url,"'>",state,"</a>")) %>%
  select(state_page_link,url)

kable(links_table,escape = FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) 
```